Evaluating Sound Similarity Metrics for Differentiable, Iterative Sound-Matching

### 2025-09-26 review_responses.tex

\begin{displayquote}
    At a glance, our methodology is to conduct controlled, low-level differentiable experiments—without proxy networks—by pairing four DSP-based synthesizers with four differentiable loss functions. We optimize parameters directly via gradients in order to isolate loss–synthesizer interactions. This controlled setup systematically evaluates the performance of iterative sound-matching pipelines, where “performance” is defined as the similarity of the synthesized output to a target. Similarity is assessed with P-Loss, MSS, and—most importantly—manual listening tests. This design allows us to directly test our central hypothesis: that the effectiveness of a loss function depends on the synthesis method, and that no universal “best” similarity measure exists.
\end{displayquote}

\subsection*{R2.2 Relation to Prior Work}
\noindent \textbf{The authors claim that differentiable iterative sound matching is largely unexplored, but prior work (Barkan et al., Cherep et al.) could be considered in this category.}\\

\noindent\textbf{Response:} \\
We thank the reviewer for pointing out sound-matching works that match the ``differentiable and iterative'' description, but were not covered in our literature review. We believe that the term ``under-explored'' is perhaps more appropriate. We've added these works to \textbf{Table 1} which provides a summary of notable previous work, and discussed them in more detail in the final paragraphs of \textbf{II.F Historical Framing of Sound-Matching}: 
\begin{itemize}
  \item \textbf{Barkan et al.:} Their work relies on neural proxies for the synthesizer, with inference-time finetuning of the encoder. This constitutes iterative optimization, but the optimization occurs on an approximate model rather than directly on differentiable DSP functions. By contrast, our approach avoids proxy error and directly analyzes how losses behave relative to known synthesis structures.  
  \item \textbf{Cherep et al.:} Their work uses CLAP embeddings with evolutionary search for text-to-audio tasks. While applicable to audio-to-audio matching, CLAP acts as a black-box representation and does not isolate loss--synth interactions. Our approach is complementary, focusing on controlled experiments with simple differentiable DSP synthesizers to expose the strengths and weaknesses of different similarity measures.  In addition, embedding models such as CLAP use simpler representations at their core---commonly Fourier transformations---and our work explores the low level functions that are often used for the training of embedding models.
\end{itemize}
Looking at these works, we see that our contribution is distinct: we provide the missing \textbf{low-level benchmarking} of loss functions across multiple synthesis methods, which is not addressed by proxy-based or embedding-based approaches.

\subsection*{R2.3 Clear Takeaways}
\noindent\textbf{Review:}
\textbf{This work addresses the problems on ``Loss Selection'' and ``Synthesis Selection.''  However, the results as presented here are largely inconclusive (i.e. it is not imminently clear how to select losses/synthesizer pairings), leaving very little in the way of clear takeaways sparking future research.\\}

\noindent\textbf{Response:} \\

We acknowledge the reviewer’s concern that our main result may appear inconclusive. However, we see this as an important finding in itself: much of the prior literature implicitly over-claims general effectiveness of particular loss functions based on narrow or in-domain settings. Our revisions now explicitly emphasize that the lack of a “silver bullet” for loss functions is a core contribution of this work. By showing that loss effectiveness depends on the synthesis context, the inconclusiveness can be seen as evidence against over-generalization, and an argument for more thorough, context-sensitive benchmarks in measuring sound similarity.\\

As for clear takeaways, we've added two new sections which address the valid issues raised here and by Reviewer 1.

\begin{itemize}
  \item \textbf{IV.B Practical Recommendations} which distills our findings into actionable guidlines for practitioners. DTWEnv is recommended for amplitude-modulated synthesis, SIMSE for subtractive/noise-filtered synthesis, and MSS or P-Loss as large-scale proxies for sound-matching evaluation (with manual validation being strongly advised). We also note that our results challenge prior claims about JTFS’s universal superiority for mesostructures.
  \item \textbf{IV.D Applicability to More Complex Synthesizers} that explicitly discusses how the insights from our controlled two-parameter DSP-based synthesizers generalize to richer synthesizers with many parameters and complex routing. While acknowledging the limitations of our simplified testbed, we argue that the observed dependencies between synthesis method and loss function remain informative even in more complex settings.
\end{itemize}
For a more detailed response, see our response to the Reviewer.1 in Sections~\nameref{R1.6} and \nameref{R1.7}. Our response to \nameref{R1.5} may also be of interest.

\section{Reviewer 4}
\subsection{Use of Appropriate Symbols}
\noindent\textbf{Review:}
The notation \textbf{[for the equation introduced in II.A]} is confusing. In the manuscript, $t$ is used to denote the target sound, but in audio/signal processing $t$ usually represents time.  
A clearer alternative would be to write $x_\theta$ and $x_0$, so that $x$ always denotes a sound waveform, with the subscript indicating whether it is generated from parameters $\theta$ or given as the target.  
This avoids overloading $t$ and improves readability.

\noindent\textbf{Response:}
This is a helpful suggestion, and we have made the switch from $x$ and $t$ to $x_{\theta}$ and $x_0$.

\section{Optimal Targets}
\noindent\textbf{Review:}
You mentioned "There is no optimal or correct version of an 8-bit snare sound".
This statement is true when you are given only the text description of the sound. However, if you have the target sound $x_0$  the target sound itself is "correct", isn't it? So your hypothesis only holds if you don't have the target sound but the text description, am I understanding it correctly?

\noindent\textbf{Response:}

\subsection{STFT Losses and Time-Shifts}
\noindent\textbf{Review:}
"If one of these tones is slightly shifted in time, then the spectrogram will no longer overlap". This is true if we don't apply any techniques like DTW to realign them, right?
So the STFT losses doesn't work for the cases where there's time shift?

\noindent\textbf{Response:}

\subsection{Can We Overfit?}
\noindent\textbf{Review:}
One final question that is just out of curiosity.
In your iterative algorithm, you always run it for 200 steps, right?
In my field of machine learning, if we set 200 steps, the result in the final step might not be the optimal one due to overfitting. So sometimes we obtain the optimal results at around 100 steps, and the model gets worse after this.
Do you have the same thing in your algorithm? Or the final step is always the best step?

\noindent\textbf{Response}

\subsection{Minor Edits}
\noindent\textbf{Review}
Isn't it better to move the symbol explanation earlier to where the first equation is? I could only under the equations after reading section C.

\noindent\textbf{Response:}
We have moved symbol explanations right after the introduction in 
\textbf{II. A Formalization of Sound-Matching}.

\noindent\textbf{Review:}
"out-of-domain sounds is an unexplored area". Unexplored means no one has done it before to me. But in Table 1, you have already cited a few work that tried to do it. So, should it be "underexplored" instead of "unexplored"?

\noindent\textbf{Response:}

\noindent\textbf{Review:}
You mentioned "four different synthesizers" here, but you never elaborate on which four, not until page 8. Probably you can specify the four synthesizers earlier?

\noindent\textbf{Review:}
You described the Likert scale from 1 to 5 here. But in the next paragraph, you describe the Likert scores again. Not sure if I misunderstood anything, but It looks a bit redundant to me. Would it be possible to combine both to reduce redundancy?

\noindent\textbf{Review:}
Just a minor grammar question, Is there a missing subject in the first sentence?While [we] cannot prove ...

\noindent\textbf{Review:}
